Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-23 manuscript/draft.Rmd
Minor wording suggestions
Tweaks of Ethan's wording in 2 places

Biodiversity forecasts are important for conservation, management, and
evaluating how well current models characterize natural systems. While the
number of forecasts for biodiversity are increasing, there is little information
available on how well these forecasts work. Most biodiversity forecasts are not
evaluated to determine how well they predict future diversity, fail to account
for uncertainty, and do not use time-series data that captures the actual
dynamics being studied. We addressed these limitations by using best practices
to explore our ability to forecast the species richness of breeding birds in
North America. We used hindcasting to evaluate six different modeling approaches
for predicting richness. Hindcasts for each method were evaluated annually for a
decade at `r numbers$N_predict_sites` sites distributed throughout the
continental United States. While each model could explain most of the variance
in richness, none of them consistently outperformed a baseline model that
predicted constant richness at each site. In particular, we found no evidence
that current methods (such as species distribution models) can successfully turn
spatial data into useful temporal predictions about biodiversity at decadale
time-scales. The best practices implemented in this study directly influence the
forecasts, the relative performance of different modeling approaches, and the
conclusions about the current state of biodiversity forecasting . To facilitate
the rapid improvement of biodiversity forecasts, we emphasize the value of
specific best practices in making forecasts and evaluating forecasting methods.

@@

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models
[SDMs; @thomas2004; @urban2015]. In general, these models describe individual
species' occurrence patterns as functions of the environment. Predictions about
where each species will occur in the future are made by using forecasts of
future environmental conditions to generate predictions from these models. These
species-level predictions are then combined ("stacked") to generate forecasts
for species richness [e.g. @calabrese2014]. Alternatively, models that directly
relate spatial patterns of species richness to environment conditions have been
developed and generally perform equivalently to stacked SDMs [@algar2009;
@distler2015]. This approach is sometimes referred to as "macroecological"
modeling, because it models the larger-scale pattern (richness) directly
[@distler2015].

>>>>

Biodiversity forecasts are important for conservation, management, and
evaluating how well current models characterize natural systems. While the
number of forecasts for biodiversity is increasing, there is little information
available on how well these forecasts work. Most biodiversity forecasts are not
evaluated to determine how well they predict future diversity, fail to account
for uncertainty, and do not use time-series data that captures the actual
dynamics being studied. We addressed these limitations by using best practices
to explore our ability to forecast the species richness of breeding birds in
North America. We used hindcasting to evaluate six different modeling approaches
for predicting richness. Hindcasts for each method were evaluated annually for a
decade at `r numbers$N_predict_sites` sites distributed throughout the
continental United States. While each model could explain most of the variance
in richness, none of them consistently outperformed a baseline model that
predicted constant richness at each site. In particular, we found no evidence
that current methods (such as species distribution models) can successfully turn
spatial data into useful temporal predictions about biodiversity at decadale
time-scales. The best practices implemented in this study directly influence the
forecasts, the relative performance of different modeling approaches, and the
conclusions about the current state of biodiversity forecasting . To facilitate
the rapid improvement of biodiversity forecasts, we emphasize the value of
specific best practices in making forecasts and evaluating forecasting methods.

@@

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models
[SDMs; @thomas2004; @urban2015]. In general, these models describe individual
species' occurrence patterns as functions of the environment. Given forecasted
environmental conditions, these models can predict where each species will occur 
in the future. These species-level predictions are then combined ("stacked") to 
generate forecasts for species richness [e.g. @calabrese2014]. Alternatively, 
models that directly relate spatial patterns of species richness to environment 
conditions have been developed and generally perform equivalently to stacked SDMs 
[@algar2009; @distler2015]. This approach is sometimes referred to as 
"macroecological" modeling, because it models the larger-scale pattern (richness) 
directly [@distler2015].
